---
title: "Career Center Review"
description: |
  Below is an analysis of the levels of satisfaction for various GVSU career center services. 
author:
  - name: Debit and Jae Mwangi
    url: {}
date: 11-30-2021
output:
  distill::distill_article:
    self_contained: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

The results revealed that GVSU graduates had a general sense of satisfaction with the Career Center services across the board.

```{r}
library(tidyverse)
library(dplyr)
test_alumni <- read_csv("data/alumni_data.csv")
grouped_CC_review<-test_alumni %>% 
  group_by(CC_job_Rating) %>% 
    filter(CC_job_Rating !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))

temp1<-test_alumni %>% 
  group_by(CC_Drop_in_Advising_CareerLab) %>% 
  summarise(n = n()) %>%
  filter(CC_Drop_in_Advising_CareerLab !="NA")%>% 
arrange(desc(n))
temp1<-temp1%>%rename(CC_job_Rating= CC_Drop_in_Advising_CareerLab) 
everything <-rbind(grouped_CC_review,temp1)

temp2<-test_alumni %>% 
  group_by(CC_Handshake_Jobs) %>% 
  filter(CC_Handshake_Jobs !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))
temp2<-temp2%>%rename(CC_job_Rating= CC_Handshake_Jobs) 
everything <-rbind(everything,temp2)

temp3<-test_alumni %>% 
  group_by(CC_Interview_Preparation) %>% 
  filter(CC_Interview_Preparation !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))
temp3<-temp3%>%rename(CC_job_Rating= CC_Interview_Preparation) 
everything <-rbind(everything,temp3)
everything<-everything%>%rename(Ratings= CC_job_Rating) 
everything$Question <- c('Job Search'
                            ,'Job Search'
                            ,'Job Search'
                            ,'Job Search'
                            ,'Job Search'
                           
                            ,'Drop in Advising'
                            ,'Drop in Advising'
                            ,'Drop in Advising'
                            ,'Drop in Advising'
                            ,'Drop in Advising'
                           
                            
                            ,'Handshake Jobs'
                            ,'Handshake Jobs'
                            ,'Handshake Jobs'
                            ,'Handshake Jobs'
                            ,'Handshake Jobs'
                         
                            ,'Interview Prepartion'
                            ,'Interview Prepartion'
                            ,'Interview Prepartion'
                            ,'Interview Prepartion'
                            ,'Interview Prepartion'
                         
                            
                            
)
everything %>%
  ggplot(aes(x=forcats::fct_reorder(Question,n),y=n, fill=Ratings)) +
  geom_col() + 
  coord_flip() + 
  labs(x="Review Categories", y="Number of Participants")
```

It was observed that most GVSU graduates had utilized the career center job and internship search services as well as the handshake job search web application to obtain employment after graduation.
However, results showed that only about half of the 4000 respondents leveraged career center workshops and only a little over a half utilized on-campus interview practice offered by the career center. 

```{r}
grouped_CC_review1<-test_alumni %>%  
  group_by(CC_Oncampus_Interview) %>% 
    filter(CC_Oncampus_Interview !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))

temp3<-test_alumni %>% 
  group_by(CC_Networking_Strategies) %>% 
  summarise(n = n()) %>%
  filter(CC_Networking_Strategies !="NA")%>% 
arrange(desc(n))
temp3<-temp3%>%rename(CC_Oncampus_Interview= CC_Networking_Strategies) 
everything2 <-rbind(grouped_CC_review1,temp3)

temp4<-test_alumni %>% 
  group_by(CC_Career_Major_Exploration) %>% 
  filter(CC_Career_Major_Exploration !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))
temp4<-temp4%>%rename(CC_Oncampus_Interview= CC_Career_Major_Exploration) 
everything2 <-rbind(everything2,temp4)

temp5<-test_alumni %>% 
  group_by(CC_Fairs_Career_Events) %>% 
  filter(CC_Fairs_Career_Events !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))
temp5<-temp5%>%rename(CC_Oncampus_Interview= CC_Fairs_Career_Events) 
everything2<-rbind(everything2,temp5)

everything2<-everything2%>%rename(Ratings= CC_Oncampus_Interview) 
everything2$Question <- c('Oncampus Interview'
                            ,'Oncampus Interview'
                            ,'Oncampus Interview'
                            ,'Oncampus Interview'
                            ,'Oncampus Interview'
                           
                            ,'Networking Strategies'
                            ,'Networking Strategies'
                            ,'Networking Strategies'
                            ,'Networking Strategies'
                            ,'Networking Strategies'
                           
                            
                            ,'Career & Major Exploration'
                            ,'Career & Major Exploration'
                            ,'Career & Major Exploration'
                            ,'Career & Major Exploration'
                            ,'Career & Major Exploration'
                         
                            ,'Fairs & Career Events'
                            ,'Fairs & Career Events'
                            ,'Fairs & Career Events'
                            ,'Fairs & Career Events'
                            ,'Fairs & Career Events'
                         
                            
                            
)
everything2 %>%
  ggplot(aes(x=forcats::fct_reorder(Question,n),y=n, fill=Ratings)) +
  geom_col() + 
  coord_flip() + 
  labs(x="Review Categories", y="Number of Participants")
```

This revealed the gap that exists in students making time to attend career workshops as well as the under-utilization of interview preparation services offered by the career center. 

```{r}
grouped_CC_review2<-test_alumni %>%  
  group_by(CC_Resume_Cover_Letter_Review) %>% 
    filter(CC_Resume_Cover_Letter_Review !="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))

temp6<-test_alumni %>% 
  group_by(CC_Career_Assessments) %>% 
  summarise(n = n()) %>%
  filter(CC_Career_Assessments !="NA")%>% 
arrange(desc(n))
temp6<-temp6%>%rename(CC_Resume_Cover_Letter_Review= CC_Career_Assessments) 
everything3 <-rbind(grouped_CC_review2,temp6)

temp7<-test_alumni %>% 
  group_by(CC_Workshops) %>% 
  filter(CC_Workshops!="NA")%>% 
  summarise(n = n()) %>%
arrange(desc(n))
temp7<-temp7%>%rename(CC_Resume_Cover_Letter_Review= CC_Workshops) 
everything3<-rbind(everything3,temp7)

everything3<-everything3%>%rename(Ratings= CC_Resume_Cover_Letter_Review) 
everything3$Question <- c('Resume & Cover Letter Review'
                            ,'Resume & Cover Letter Review'
                            ,'Resume & Cover Letter Review'
                            ,'Resume & Cover Letter Review'
                            ,'Resume & Cover Letter Review'
                           
                            ,'Career Assessment'
                            ,'Career Assessment'
                            ,'Career Assessment'
                            ,'Career Assessment'
                            ,'Career Assessment'
                           
                            
                            ,'Workshops'
                            ,'Workshops'
                            ,'Workshops'
                            ,'Workshops'
                            ,'Workshops'
                            
                            
)
everything3 %>%
  ggplot(aes(x=forcats::fct_reorder(Question,n),y=n, fill=Ratings)) +
  geom_col() + 
  coord_flip() + 
  labs(x="Review Categories", y="Number of Participants")
```
Therefore, we encourage all students to maximize the use of the career center services to prepare themselves for the job market.
